Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-18 draft.tex
typo

We now show how to optimize $\PMR$.
In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
%We also have numerical variables to represent the weights of the scoring rule.
Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
Since we know that $x$ and $y$ are ranked $\gamma{j}$ positions apart, we set the constraint:
$B_{i+\gamma{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.

>>>>

We now show how to optimize $\PMR$.
In addition to variables $\{ w_{j} \}_{j=1,\ldots,m}$ (one for each position) we need to employ several additional decision variables.
We introduce two sets of binary variables $B^{+}_{i,j}$ and $B^{-}_{i,j}$  for each position $i$ and for each voter $j$.
Variable $B_{i,j}^{+}$ encodes the fact that the alternative $y$ is placed in position $i$ in the ranking of agent $j$; while  $B_{i,j}^{-}$ encodes the same thing for alternative $x$.
%We also have numerical variables to represent the weights of the scoring rule.
Since each alternative needs to be placed exactly in one place for each agent, we adopt the constraints
$\sum_{i=t_{1}(j)}^{t_{2}(j)} B_{i,j}^{+} = 1$.
Since we know that $x$ and $y$ are ranked $\gamma_{j}$ positions apart, we set the constraint:
$B_{i+\gamma_{j},j}^{-} \geq B_{i,j}^{+}$,  for $i = \{ t_{1}(j), \ldots, t_{2}(j)\}$.
